### 2015-05-12 whoop.tex
created draft paragraph for identifying locks

\ADComment{Explain how we identify mutexes (inside our Boogie-based analysis)}

\medskip\noindent\textbf{Instrumentation and Analysis }
%
The core \whoop tool (see Figure~\ref{fig:whoop} -- B) is responsible for parsing, instrumenting and sequentializing the abstract Boogie program. During the initial parsing, \whoop performs a static analysis (on the Boogie IVL code) to identify all lock identifiers and rewrite them to a unique constant Boogie variable, e.g. the following call to \texttt{mutex\_lock()}:

@@

When the lock rewriting finishes, \whoop traverses the Boogie IVL code, uses the information extracted by Chauffeur and separates each independent entry point call-graph from the rest of the program. To achieve this, it duplicates helper functions and renames them accordingly: e.g. for entry point \texttt{ep1}, a helper function \texttt{foo} will be renamed to \texttt{foo\$ep1}. This allows \whoop to perform entry point sensitive instrumentation and analysis. Although the program can potentially become much larger, this does not affect the analysis as discussed later.

Next, \whoop instruments the program with global variables for lockset analysis and race-checking per entry point. For example, for entry point \texttt{ep1}, \whoop instruments:

>>>>

\medskip\noindent\textbf{Identifying Set of Locks }
%
\whoop performs a static analysis (on the Boogie IVL code) to identify all lock identifiers and rewrite them to a unique constant Boogie variable, e.g. the following call to \texttt{mutex\_lock()}:

@@

\medskip\noindent\textbf{Instrumentation and Analysis }
%
Next, \whoop instruments the program with global variables for lockset analysis and race-checking per entry point. For example, for entry point \texttt{ep1}, \whoop instruments:
